Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-07 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:07	14:29:15	(Mon 7.Sep)

The results will be presented in the following order: In section \ref{lca_window_function} we discuss typical window responses computed by MVDR (\Fig{mvdr_selected_windows}), and hypothesize  that these can be mimicked by Kaiser windows. In section \ref{lca_kaiser_parameters} we investigate what sensible boundaries for the Kaiser parameter $\beta$ and window steering $\phi$ should be (\ref{oversampling_mosaic_bounds}).

@@

\subsection{Window database size}

>>>>

The results will be presented in the following order: In section \ref{lca_window_function} we discuss typical window responses computed by MVDR (\Fig{mvdr_selected_windows}), and hypothesize  that these can be mimicked by Kaiser windows. In section \ref{lca_kaiser_parameters} we investigate what sensible boundaries for the Kaiser parameter $\beta$ and window steering $\phi$ should be (\Fig{oversampling_mosaic_bounds}). In section \ref{lca_database_size} we discuss how many variations of windows between the just determined boundaries should be (\Fig{oversampling_mosaic_bounds_beta}), and determine max window database size.

@@

\subsection{Window database size}\label{lca_database_size}
